Quality Assesment of OpenStreetMap Footpath Data

### 2020-06-17 report/report.tex
Add road collision case figure to report

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{img_road_error_cases}
    \caption{Example segments of a 3D reconstruciton of the Stockholm road map, with clearly visible geometric errors. The road overlap is marked with red boundaries. The segments show firstly a healthy intersection with main car roads, sidewalks and pedestrian crossings (top left), secondly a city segment where roads have been placed so they overlap with existing buildings due to insufficient data precision (top right), thirdly a similar case where roads overlap with each other (bottom left) and lastly an intersection where the road geomerty twists and self-intersects in strange ways due to invalid source data. This last case will not be examined in this project.}
    \label{fig:residential-footpath-map}
\end{figure}
